---
title: "Model Fit"
#output: pdf_document
output: latex_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(lme4)
```

# Goodness of fit

Body mass is divided into size classes that are the log10(mass).

## Speed

```{r, echo=FALSE}
setwd("~/Master_Uottawa/Functional_Response/Manuscript/FEE_Paper/Manuscript/Review/Fitting")
speed = read.csv('Speed.csv',colClasses = c('numeric','numeric','numeric','factor'))

speed5 = which(speed$LogSize==5)
speed$LogSize[speed5] = 4
speed = droplevels(speed)

speed$log10pred_log10obs = log10(speed$Predicted) - log10(speed$Observed)

mod1 = lm(log10pred_log10obs~log10(Predicted)*LogSize,data=speed)
summary(mod1)

```
The slope does not significantly differ from 1 and the intercept from 0.
The model does not show any significant effect of size.

## Attack rate
### Linear model of oberved versus predicted data (with size as cofactor)
```{r, echo=F}
dat = read.csv('DataFitting.csv',colClasses = c('numeric','numeric','numeric','factor','factor','factor'))
capture = subset(dat,dat$Trait=='Probability')
capture = droplevels(capture)
attack = subset(dat,dat$Trait=='Attack')
attack = droplevels(attack)
toto = which(attack$Predicted==0)
attack = attack[-toto,]
handling = subset(dat,dat$Trait=='Handling')
handling = droplevels(handling)

attack$log10pred_log10obs = log10(attack$Predicted) - log10(attack$Observed)
handling$log10pred_log10obs = log10(handling$Predicted) - log10(handling$Observed)
capture$pred_obs = capture$Predicted - capture$Observed

mod22 = lm(log10pred_log10obs~log10(Predicted)*LogSize,data=attack)
summary(mod22)

```
The slope does not significantly differ from 1 and the intercept from 0.
The model does not show any significant effect of size, except for 10e-5 kg size range (i.e., 10 mg).

### Linear mixed model of oberved versus predicted data (with size as cofactor, and study as random effect)
```{r, echo=F}
mod2 = lmer(log10pred_log10obs~log10(Predicted)*LogSize+(1|Study),data=attack)
summary(mod2)

```
The source of data (study) does not have a significant effect.

## Capture probability
```{r,echo=F}
mod5 = lm(pred_obs~ Predicted,data=capture)
summary(mod5)

```
The slope does not significantly differ from 1 and the intercept from 0.
Size was not included as a cofactor, since size range in the dataset is narrow and unbalanced.

## Handling time
### Linear model of oberved versus predicted data (with size as cofactor)
```{r,echo=F}
mod3 = lm(log10pred_log10obs~log10(Predicted)*LogSize,data=handling)
summary(mod3)

```
The slope and the intercept significantly differ from 1 and 0 respectively.
Almost all size ranges show a significant effect.

### Linear mixed model of oberved versus predicted data (with size as cofactor, and study as random effect)
```{r,echo=F}
mod33 = lmer(log10pred_log10obs~log10(Predicted)*LogSize+(1|Study),data=handling)
summary(mod33)

```
The source of data (study) does not have a significant effect.

## Plots
```{r, echo=F}
par(mar=c(5,5,4,1))
plot(log10(speed$Observed)~log10(speed$Predicted),xlab='Predicted',ylab='Observed',main = 'Speed',cex.lab=1.5,
     ylim = c(-1.2,1.6),xlim = c(-1.2,1.6))
abline(a = 0, b = 1,lwd=3)
plot(log10(attack$Observed)~log10(attack$Predicted),xlab='Predicted',ylab='Observed',main = 'Attack rate',cex.lab=1.5,
     xlim = c(-12.5,-3), ylim = c(-12.5,-3))
abline(a = 0, b = 1,lwd=3)
plot(capture$Observed~capture$Predicted,xlab='Predicted',ylab='Observed',main = 'Capture probability',cex.lab=1.5,
     xlim = c(0,1))
abline(a = 0, b = 1,lwd=3)
plot(log10(handling$Observed)~log10(handling$Predicted),xlab='Predicted',ylab='Observed',main = 'Handling time',cex.lab=1.5,xlim = c(-5,7), ylim = c(-5,7))
abline(a = 0, b = 1,lwd=3)
```
